---
title: "Cabbages"
author: "Larissa Vera!"
date: "Fall 2024"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy.
Complete this report by answering the following two questions  
 
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?

$H_0$: There is no difference in average VitC between c39 and c52 cultivation methods

$H_A$: Statistically there is a difference in average VitC between c39 and c52 cultivation.


# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

I predict that VitC is a numerical variable and cultivation is categorical. So the helper file used is num~ categorical.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```

The boxplot shows that the c52 method has higher levels of VitC than the c39 method.

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The numerical summary shows that c52 method has about 15% more than c39 method.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

We reject the hypothesis because the P value is 3.405e-08 which is less than 0.05. The VitC c52 method has higher levels than the c39 method.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The hypothesis is rejected due to the p value being 3.405e-08. The data was retrieved from the helper file num~cat. In conclusion the VitC c52 has higher levels vs c39.
